The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2020-06-15 Fsing/FrobeniusThresholdsPaper/response_to_report_C_on_v2.txt

We thank the referee for carefully checking the package, paper, and
documentation, and for the helpful suggestions and corrections.

Below we address in detail each of the refereee's comments.

### 2020-06-16 Fsing/FrobeniusThresholdsPaper/response_to_report_C_on_v2.txt

-----------------------------------------------------------------------------
Done.
-----------------------------------------------------------------------------

*****************************************************************************

Consider choosing a better name for the function "nu", which is simply the
English spelling of a random Greek letter, and thus is not descriptive.
Something with words in it, such as "containmentPower", or even "index".

-----------------------------------------------------------------------------
We replaced "nu" with "frobeniusNu", which, although still not descriptive,
at least establishes a context. Having "Nu" as part of the name allows the
user to relate this to the terminology/notation used in the literature.
-----------------------------------------------------------------------------

@@

*****************************************************************************

Consider renaming "fpt" to "pureThreshold" and "isFPT" to "isPureThreshold".
(The "F" for "Frobenius" can be assumed.)

-----------------------------------------------------------------------------
We chose to leave it unchanged, as "fpt" is a very standard abbreviation.
-----------------------------------------------------------------------------

### 2020-06-16 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Replaced nu with frobeniusNu

\section{The {\tt nu} function}
\label{sec.Nu}

We first describe the \texttt{nu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
We adopt the setup established in the introduction: we work in a polynomial ring $R$ over a finite field of characteristic $p>0$,  $\idealm$ denotes the ideal generated by the variables, and $e$ is a natural number.
If $I$ and $J$ are ideals of $R$, the command \texttt{nu(e,I,J)} outputs the extended integer $\nu_I^J(p^e)$ defined in the introduction; if $f$ is an element of $R$, \texttt{nu(e,f,J)} outputs $\nu_f^J(p^e) \coloneqq \nu_{\langle f \rangle}^J(p^e)$.
When the third argument is omitted from the function \texttt{nu}, it is assumed to be the maximal ideal $\idealm$.

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y];

@@

i4 : nu(2, I, J)

@@

i6 : nu(2, f, J)

o6 = 120
\end{MyVerbatim}
}

In general, the function \texttt{nu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
It is well known that, for any positive integer $e$,
\[ \nu_I^J(p^e) = \nu_I^J(p^{e-1})\cdot p + L,\]
where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
This implies that when searching for the maximal exponent defining \texttt{nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{nu(e-1,I,J)}, and one need not search too far past this number.
% This also suggests that the most efficient way to compute \texttt{nu(e,I,J)} is to compute, successively, \texttt{nu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.

\subsection{Options for \texttt{nu}}

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i7 : R = ZZ/5[x,y,z];

@@

i9 : time nu(2, m, m^2)
     -- used 1.82479 seconds

o9 = 97
\end{MyVerbatim}
}
%\medskip
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i10 : time nu(2, m, m^2, Search => Linear)
     -- used 0.597035 seconds

o10 = 97
\end{MyVerbatim}
}
\smallskip

%We now describe the options available for the function \texttt{nu}.

If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, \texttt{nu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.

% \medskip
\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i11 : nu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)

@@

o11 : List
\end{MyVerbatim}
}
%\medskip
\smallskip

@@

As described in the introduction, the integer $\nu_I^J(p^e)$ is the maximal integer $n$ such that the $n$-th power of $I$ is not contained in the $p^e$-th Frobenius power of $J$.  However,
\begin{equation*}
  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J,
\end{equation*}
where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
The option \texttt{ContainmentTest} for \texttt{nu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.

If \texttt{ContainmentTest} is set to \texttt{StandardPower}, then \texttt{nu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to \texttt{FrobeniusRoot}, the right-hand containment is checked.
For efficiency reasons, the default value for \texttt{ContainmentTest} is set to  \texttt{FrobeniusRoot} if the second argument passed to \texttt{nu} is a polynomial, and is set to \texttt{StandardPower} if the second argument is an ideal.

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i12 : R = ZZ/11[x,y,z];

@@

i14 : time nu(3, f) 
     -- used 0.153691 seconds

o14 = 1209
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i15 : time nu(3, f, ContainmentTest => StandardPower)
     -- used 10.1343 seconds

o15 = 1209
\end{MyVerbatim}
}
\smallskip

The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which allows \texttt{nu} to compute a different but analogous invariant.
The first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of an ideal $I$, when $n$ is an arbitrary nonnegative integer \cite{hernandez+etal.frobenius_powers}.
When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{nu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.  This number is denoted $\mu_I^J(p^e)$ in \emph{loc.~cit.}, and equals $\nu_I^J(p^e)$ when $I$ is a principal ideal.
However, these numbers need not agree in general, as we see below.

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i16 : R = ZZ/3[x,y];

@@

i18 : nu(4, m^5)

@@

i19 : nu(4, m^5, ContainmentTest => FrobeniusPower)

o19 = 26
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i20 : R = ZZ/17[x,y,z];

@@

i22 : time nu(10, f)
     -- used 0.0161622 seconds

@@

i23 : time nu(10, f, UseSpecialAlgorithms => false)
     -- used 2.06877 seconds

o23 = 1541642394460
\end{MyVerbatim}
}
\smallskip

The last option we describe for \texttt{nu} is \texttt{AtOrigin}.
Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), the function \texttt{nu} determines, instead, the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is the unit ideal, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i24 : R = ZZ/7[x,y];

@@

i26 : nu(3, f)

@@

i27 : nu(3, f, AtOrigin => false)

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z]/(x^2 - y*(z - 1));

@@

o4 = false
\end{MyVerbatim}
}

\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i5 : R = ZZ/13[x,y];

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];

@@

In the following example, we compute the $F$-pure threshold of a diagonal polynomial.

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i4 : fpt(x^17 + y^20 + z^24)

@@

More specifically, let $e$ denote the value of the option \texttt{DepthOfSearch}, which conservatively defaults to \texttt{1}.
The \texttt{fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of \texttt{nu(e,f)}.
It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition~4.2]{HernandezFPurityOfHypersurfaces} to the lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
%
\begin{equation}
\label{estimating-interval: e}
\tag{$\dagger$}
\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
\end{equation}

@@

o10 : List
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i11 : fpt(f, Attempts => 0, DepthOfSearch => 3)

@@

o11 : List
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i12 : fpt(f, Attempts => 1, DepthOfSearch => 3)

@@

o12 : QQ
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;

@@

o14 : List
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i15 : fpt(f, Attempts => 2, DepthOfSearch => 3)

@@

o15 : QQ
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i16 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

@@

o19 : QQ
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i20 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;

@@

o22 : List
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i23 : f = 2*x^10*y^8 + x^4*y^7 - 2*x^3*y^8;

@@

o24 : List
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i25 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)

@@

o25 : List
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i26 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
     -- used 0.72874 seconds

@@

o28 : QQ
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i29 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
Starting fpt ...
fpt is not 1 ...
Verifying whether special algorithms apply...
Special fpt algorithms were not used ...
ν has been computed: ν = nu(3,f) = 17 ...
fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [17/124,18/125] ...
Starting guessFPT ...
The right-hand endpoint is not the fpt ...
The left-hand endpoint is not the fpt ...
guessFPT narrowed the interval down to (7/50,18/125) ...
Beginning F-signature computation ...
First F-signature computed: s(f,(ν-1)/p^e) = 793/15625 ...
Second F-signature computed: s(f,ν/p^e) = 342/15625 ...
Computed F-signature secant line intercept: 8009/56375 ...
F-signature intercept is an improved lower bound;
Using F-regularity to check if it is the fpt ...
The new lower bound is not the fpt ...
fpt failed to find the exact answer; try increasing the value of
    DepthOfSearch or Attempts.
fpt lies in the interval (8009/56375,18/125).

@@

o29 : List
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i30 : R = ZZ/7[x,y];

@@

o33 : QQ
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i34 : R = ZZ/7[x,y,z];

@@

o36 = false
\end{MyVerbatim}
}
\smallskip

@@

\smallskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i37 : R = QQ[x,y,z];

@@

o40 = false
\end{MyVerbatim}
}
\smallskip

>>>>

\section{The {\tt frobeniusNu} function}
\label{sec.Nu}

We first describe the \texttt{frobeniusNu} function, a fundamental component of the package \emph{FrobeniusThresholds}.
We adopt the setup established in the introduction: we work in a polynomial ring $R$ over a finite field of characteristic $p>0$,  $\idealm$ denotes the ideal generated by the variables, and $e$ is a natural number.
If $I$ and $J$ are ideals of $R$, the command \texttt{frobeniusNu(e,I,J)} outputs the extended integer $\nu_I^J(p^e)$ defined in the introduction; if $f$ is an element of $R$, \texttt{frobeniusNu(e,f,J)} outputs $\nu_f^J(p^e) \coloneqq \nu_{\langle f \rangle}^J(p^e)$.
When the third argument is omitted from the function \texttt{frobeniusNu}, it is assumed to be the maximal ideal $\idealm$.

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y];

@@

i4 : frobeniusNu(2, I, J)

@@

i6 : frobeniusNu(2, f, J)

o6 = 120
\end{MyVerbatim}
}
\bigskip

In general, the function \texttt{frobeniusNu} works by searching through a list of integers $n$, and checking containments of the $n$-th power of $I$ in the specified Frobenius power of $J$.
It is well known that, for any positive integer $e$,
\[ \nu_I^J(p^e) = \nu_I^J(p^{e-1})\cdot p + L,\]
where the error term $L$ is nonnegative and can be explicitly bounded from above in terms of $p$ and the number of generators of $I$ and $J$.
For instance, the error term $L$ is at most $p-1$ when $I$ is principal and $J$ is arbitrary.
This implies that when searching for the maximal exponent defining \texttt{frobeniusNu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of \texttt{frobeniusNu(e-1,I,J)}, and one need not search too far past this number.
% This also suggests that the most efficient way to compute \texttt{frobeniusNu(e,I,J)} is to compute, successively, \texttt{frobeniusNu(s,I,J)}, for each integer $s = 0,\ldots,e$, and this is indeed how the computation is done in most cases.

\subsection{Options for \texttt{frobeniusNu}}

@@

\bigskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i7 : R = ZZ/5[x,y,z];

@@

i9 : time frobeniusNu(2, m, m^2)
     -- used 1.82479 seconds

o9 = 97
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i10 : time frobeniusNu(2, m, m^2, Search => Linear)
     -- used 0.597035 seconds

o10 = 97
\end{MyVerbatim}
}
\medskip

%We now describe the options available for the function \texttt{frobeniusNu}.

If the option \texttt{ReturnList} is changed from its default value of \texttt{false} to \texttt{true}, \texttt{frobeniusNu} outputs a list of the values $\nu_I^J(p^s)$, for $s=0,\ldots,e$, at no additional computational cost.

% \medskip
\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i11 : frobeniusNu(5, x^2*y^4 + y^2*z^7 + z^2*x^8, ReturnList => true)

@@

o11 : List
\end{MyVerbatim}
}
\medskip

@@

As described in the introduction, the integer $\nu_I^J(p^e)$ is the maximal integer $n$ such that the $n$-th power of $I$ is not contained in the $p^e$-th Frobenius power of $J$.  However,
\begin{equation*}
  I^n \subseteq J^{[p^e]} \Longleftrightarrow (I^n)^{[1/p^e]} \subseteq J,
\end{equation*}
where $(I^n)^{[1/p^e]}$ denotes the $p^e$-th \emph{Frobenius root} of $I^n$, as defined in \cite{BlickleMustataSmithDiscretenessAndRationalityOfFThresholds}.
The option \texttt{ContainmentTest} for \texttt{frobeniusNu} allows the user to choose which of the two types of containment statements appearing above to use toward the calculation of $\nu_I^J(p^e)$.

If \texttt{ContainmentTest} is set to \texttt{StandardPower}, then \texttt{frobeniusNu(e,I,J)} is computed by testing the left-hand containment above, and when it is set to \texttt{FrobeniusRoot}, the right-hand containment is checked.
For efficiency reasons, the default value for \texttt{ContainmentTest} is set to  \texttt{FrobeniusRoot} if the second argument passed to \texttt{frobeniusNu} is a polynomial, and is set to \texttt{StandardPower} if the second argument is an ideal.

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i12 : R = ZZ/11[x,y,z];

@@

i14 : time frobeniusNu(3, f) 
     -- used 0.153691 seconds

o14 = 1209
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i15 : time frobeniusNu(3, f, ContainmentTest => StandardPower)
     -- used 10.1343 seconds

o15 = 1209
\end{MyVerbatim}
}
\medskip

The option \texttt{ContainmentTest} has a third possible value, \texttt{FrobeniusPower}, which allows \texttt{frobeniusNu} to compute a different but analogous invariant.
The first, third, and fourth authors introduced the notion of a (generalized) Frobenius power $I^{[n]}$ of an ideal $I$, when $n$ is an arbitrary nonnegative integer \cite{hernandez+etal.frobenius_powers}.
When \texttt{ContainmentTest} is set to \texttt{FrobeniusPower}, rather than  computing $\nu_I^J(p^e)$, the function \texttt{frobeniusNu} computes the maximal integer $n$ for which $I^{[n]}$ is not contained in $J^{[p^e]}$.  This number is denoted $\mu_I^J(p^e)$ in \emph{loc.~cit.}, and equals $\nu_I^J(p^e)$ when $I$ is a principal ideal.
However, these numbers need not agree in general, as we see below.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i16 : R = ZZ/3[x,y];

@@

i18 : frobeniusNu(4, m^5)

@@

i19 : frobeniusNu(4, m^5, ContainmentTest => FrobeniusPower)

o19 = 26
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i20 : R = ZZ/17[x,y,z];

@@

i22 : time frobeniusNu(10, f)
     -- used 0.0161622 seconds

@@

i23 : time frobeniusNu(10, f, UseSpecialAlgorithms => false)
     -- used 2.06877 seconds

o23 = 1541642394460
\end{MyVerbatim}
}
\medskip

The last option we describe for \texttt{frobeniusNu} is \texttt{AtOrigin}.
Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
When the option \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), the function \texttt{frobeniusNu} determines, instead, the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is the unit ideal, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i24 : R = ZZ/7[x,y];

@@

i26 : frobeniusNu(3, f)

@@

i27 : frobeniusNu(3, f, AtOrigin => false)

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z]/(x^2 - y*(z - 1));

@@

o4 = false
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i5 : R = ZZ/13[x,y];

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];

@@

In the example below, we compute the $F$-pure threshold of a diagonal polynomial.

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i4 : fpt(x^17 + y^20 + z^24)

@@

More specifically, let $e$ denote the value of the option \texttt{DepthOfSearch}, which conservatively defaults to \texttt{1}.
The \texttt{fpt} function first computes $\nu=\nu_f(p^e)$, which agrees with the output of \texttt{frobeniusNu(e,f)}.
It is well known that the $F$-pure threshold of $f$ is greater than $\nu/p^e$ and at most $(\nu+1)/p^e$, and applying  \cite[Proposition~4.2]{HernandezFPurityOfHypersurfaces} to the lower bound tells us that the $F$-pure threshold of $f$ must be at least $\nu/(p^e-1)$.
In summary, we know that the $F$-pure threshold of $f$ must lie in the closed interval
%
\begin{equation}
\label{estimating-interval: e}
\tag{$\dagger$}
\left[ \frac{\nu}{p^e-1}, \frac{\nu+1}{p^e} \right].
\end{equation}

@@

o10 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i11 : fpt(f, Attempts => 0, DepthOfSearch => 3)

@@

o11 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i12 : fpt(f, Attempts => 1, DepthOfSearch => 3)

@@

o12 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i13 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;

@@

o14 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i15 : fpt(f, Attempts => 2, DepthOfSearch => 3)

@@

o15 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i16 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

@@

o19 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i20 : f = x^7*y^5*(x + y)^5*(x^2 + y^3)^4;

@@

o22 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i23 : f = 2*x^10*y^8 + x^4*y^7 - 2*x^3*y^8;

@@

o24 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i25 : numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)

@@

o25 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i26 : time numeric fpt(f, DepthOfSearch => 3, FinalAttempt => true)
     -- used 0.72874 seconds

@@

o28 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i29 : fpt(f, DepthOfSearch => 3, FinalAttempt => true, Verbose => true)
Starting fpt ...
fpt is not 1 ...
Verifying whether special algorithms apply...
Special fpt algorithms were not used ...
ν has been computed: ν = frobeniusNu(3,f) = 17 ...
fpt lies in the interval [ν/(p^e-1),(ν+1)/p^e] = [17/124,18/125] ...
Starting guessFPT ...
The right-hand endpoint is not the fpt ...
The left-hand endpoint is not the fpt ...
guessFPT narrowed the interval down to (7/50,18/125) ...
Beginning F-signature computation ...
First F-signature computed: s(f,(ν-1)/p^e) = 793/15625 ...
Second F-signature computed: s(f,ν/p^e) = 342/15625 ...
Computed F-signature secant line intercept: 8009/56375 ...
F-signature intercept is an improved lower bound;
Using F-regularity to check if it is the fpt ...
The new lower bound is not the fpt ...
fpt failed to find the exact answer; try increasing the value of
    DepthOfSearch or Attempts.
fpt lies in the interval (8009/56375,18/125).

@@

o29 : List
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i30 : R = ZZ/7[x,y];

@@

o33 : QQ
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i34 : R = ZZ/7[x,y,z];

@@

o36 = false
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\setstretch{.67}
\begin{MyVerbatim}
i37 : R = QQ[x,y,z];

@@

o40 = false
\end{MyVerbatim}
}
